### 2022-11-15 NSF2022/Description/broaderimpacts.tex
...
did broader impacts, intellectual merit, and overview

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from applied mathematics.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers
(URs) per year at Fordham University---for eight summer weeks.
The URs will collaborate directly with the PIs,
receive tutorials e.g., numerical methods,
and be guided on mathematical writing and presentation.
Fordham Mathematics recently completed a collaboration studio 
purpose-built for UR support.
Work products include a summary manuscript,
a presentation in the Fordham Undergraduate Research Symposium
and departmental seminars, and participation in a national conference.
We have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language 
\item Use machine learning to post-process data of granule dynamics
\item Investigate geometrical self-assembly and generate visualizations
\end{enumerate}
PI Ryham has worked side-by-side with dozens of
undergraduates and high-schoolers in
supported summer research, Girls in Science Technology and Mathematics,
and the Clare Boothe Luce Scholarship program
and the activity benefited their careers in
machine learning, water resources engineering, threat detection,
and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on
polling accessibility in New York City.
The PI is finishing works on energy densities for lipid  bilayers
with a recently graduated UR, now working at Raytheon Technologies.
His publications include works
with seven undegraduate coauthors
~\cite{Figueroa2012CuttingCI, RYHAM20112929, RyWaCo13, RyKlYaCo16}.

@@

\section{Intellectual Merit}
\label{sec:IntellectualMerit}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules with 
non-uniform hydrophobicity on their boundaries. The main
ingredient is a nonlocal interaction through the solution of moving
domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
distinguished limits to make connection with continuum models,
designing efficient and
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory to quantify the both the polar and nematic characteristics in the collective dynamics.
%
%The purpose of this research is to reach interesting physical phenomena
%with less computational cost than molecular dynamics, and account for
%more general features that continuum theory misses. The main ingredient
%is defining a nonlocal interaction through the solution of an elliptic
%boundary value problem that has the phenomenological characteristics of
%long-range hydrophobic attraction. This minimal model, while intuitive,
%is quite a general description of amphiphiles in solvent and gives rise
%to rich phenomena from Janus particle aggregates to correctly predicting
%elastic properties of bilayer. The technical research tasks include
%quantifying collective properties of amphiphilic ensembles, improving on
%mathematical models, efficient, high-order numerical algorithms for
%large-scale simulations, and incorporating external fields through
%electric charge.

>>>>

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from Applied Mathematics.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers
(URs) per year at Fordham University---for eight summer weeks.
The URs will collaborate directly with the PIs,
receive tutorials e.g., numerical methods,
and be guided on mathematical writing and presentation.
Fordham Mathematics recently completed a collaboration studio 
purpose-built for UR support.
Work products include a summary manuscript,
a presentation in the Fordham Undergraduate Research Symposium
and departmental seminars, and participation in a national conference.
We have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language 
\item Use machine learning and visualizations to post-process data of granule dynamics
\item Mathematical modeling of group affiliation in social science  
\end{enumerate}
PI Ryham has worked side-by-side with dozens of
undergraduates and high-schoolers in
supported summer research, Girls in Science Technology and Mathematics,
and the Clare Boothe Luce Scholarship program
and the activity benefited their careers in
machine learning, water resources engineering, threat detection,
and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on
polling accessibility in New York City.
The PI is finishing works on energy densities for lipid  bilayers
with a recently graduated UR, now working at Raytheon Technologies.
His publications include works
with seven undegraduate coauthors
~\cite{Figueroa2012CuttingCI, RYHAM20112929, RyWaCo13, RyKlYaCo16}.

@@

\section{Intellectual Merit}
\label{sec:IntellectualMerit}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules
with non-uniform hydrophobicity on their boundaries. The main ingredient
is a nonlocal interaction through the solution of moving domain elliptic
PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the
mathematical model in distinguished limits to make connections with
continuum models, designing efficient and high-order numerical
algorithms for large-scale two- and three-dimensional simulations with
confinement, and developing a kinetic theory to quantify both the polar
and nematic characteristics in the collective dynamics.

### 2022-11-15 NSF2022/Description/summary.tex
did broader impacts, intellectual merit, and overview

%This proposal aims to advance mathematical modeling and analysis of
%collective dynamics of amphiphilic self-assembly. Amphiphilic particles
%such as lipid molecules possess both hydrophobic and hydrophilic
%surfaces and self-assemble into meso/macroscopic structures such as
%micelles and bilayers of lipids. Experimentalists model self-assembly
%using Janus particles—spherical particles possessing a biphasic material
%label on either hemisphere. Janus particles have been widely used in
%soft matter physics as a model amphiphilic colloid and can be designed
%for catalytic activity or stimuli-responsive smart materials.

%Hydrophobic surfaces experience a nonadditive long-range attraction
%called the hydrophobic force. This force is a major source of
%nonspecific interactions in biology and soft matter. Despite its
%ubiquity, theoretical developments explaining its basic underlying
%principles have come relatively late. Motivated by its broad
%applicability, the PIs recently developed a novel and intuitive
%mathematical model, called the hydrophobic attraction potential model,
%based on the linear response of water to surface perturbations. This
%model was used to show, for the first time, self-assembly of Janus
%particles into vesicle-like structures using a partial differential
%equation-based particle interaction.

@@

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules with 
non-uniform hydrophobicity on their boundaries. The main
ingredient is a nonlocal interaction through the solution of moving
domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
distinguished limits to make connection with continuum models,
designing efficient and
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory to quantify the both the polar and nematic characteristics in the collective dynamics.

@@

\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from applied mathematics.

>>>>

@@

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules
with non-uniform hydrophobicity on their boundaries. The main ingredient
is a nonlocal interaction through the solution of moving domain elliptic
PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the
mathematical model in distinguished limits to make connections with
continuum models, designing efficient and high-order numerical
algorithms for large-scale two- and three-dimensional simulations with
confinement, and developing a kinetic theory to quantify both the polar
and nematic characteristics in the collective dynamics.

@@

\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from Applied Mathematics.
